Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 paper/paper.Rmd
Add codebox for bayes factor

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(dplyr)
library(xtable)
```

@@

```{r, results='asis'}
project_plan_raw <- read.csv("data/planning_and_outcomes.csv")

@@

@etz2016

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
```

@@

```{r, results='asis'}
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

```{r}
BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
```
@etz2016
